Networked Character Devices

### 2011-12-11 report/paper.tex
paper: remove language=C from the ncadmin listing
paper: nocite{*}
Modified abstract

\lstloadlanguages{C}
\lstset{
  language=C,
  basicstyle=\tiny,
  numbers=none,
  numberstyle=\footnotesize,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  float
}

@@

\title{Networked Character Devices}
\author{Monaco, Matthew \and Sayler, Andrew \and Spear, Landon
  \\ \and University of Colorado}
\date{\today}

@@

\begin{abstract}
While there are various projects which provide a network abstraction layer for
specific high-level subsystems in the Linux kernel, there aren't any low-level
general purpose solutions. Network character devices (NCD) is a system for
exporting character device drivers of a fast, local network. However NCD works
to some extent with regular files, block devices, sockets, and pipes; it is also
suitably responsive over Internet connections for many applications.
\end{abstract}

@@

\lstinputlisting[
  caption={The potential management interface for the NCD system.},
  label=lst:ncadmin
]{ncadmin.txt}

@@

\bibliography{refs}

>>>>

\lstloadlanguages{C}
\lstset{
  language=C,
  basicstyle=\tiny,
  numbers=none,
  numberstyle=\footnotesize,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  frame=none,
  frameround=tttt,
  float
}

@@

\title{Networked Character Devices}
\author{Monaco, Matthew \and Sayler, Andrew \and Spear, Landon \\
  \and University of Colorado \\
  \texttt{first.last@colorado.edu}
}
\date{\today}

@@

\begin{abstract}
While there are various projects which provide a network abstraction layer for
specific high-level subsystems in the Linux kernel, there aren't any low-level
general purpose solutions. Network character devices (NCD) is a system for
exporting character device interfaces over a network. This capability
divorces the traditional requirement that a device can only be used by
the host to which it is physically connected in favor of a model that
allows a device to be connected to one host but used by another.
In addition to networking the character device interface for which it
is optimized, NCD also works with regular files, block devices,
sockets, and pipes. We demonstrate how our NCD system works, as well
as a few examples of the unique systems that can be built atop the NCD
interface.
\end{abstract}

@@

\lstinputlisting[
  language={},
  caption={The potential management interface for the NCD system.},
  label=lst:ncadmin
]{ncadmin.txt}

@@

\nocite{*}
\bibliography{refs}
